Twists of supersymmetric gauge theories

### 2019-07-16 paper.tex

A local functional induces an endomorphism $\{I,-\}$ on the space of all local functionals $\oloc(E)$. 
It also induces an endomorphism on the larger space of {\em all} functionals $\cO(E)$. 
The classical master equation implies that the operator $Q + \{I,-\}$ squares to zero on $\cO(E)$, and hence every classical field theory defines a cochain complex
\[
\left(\cO(E), Q + \{I,-\}\right) .
\]
We will refer to this as the {\bf classical BV complex} of the theory.

@@

Note that a map of classical field theories induces a map of BV complexes
\[
F^*\colon \left(\cO (\cE)[-1], Q + \{I,-\} \right) \to \left(\cO (\cE')[-1], Q' + \{I',-\} \right) .
\]
This allows us to make the following definition of an equivalence between classical theories.

\begin{dfn} \label{equivalence_def}
A morphism of classical field theories $F\colon (E, Q, \omega, I) \to (E', Q', \omega', I')$ is an {\bf equivalence} if it induces a quasi-isomorphism 
\[
F^* \colon  \left(\cO(\cE')[-1], Q' + \{I',-\} \right) \xto{\simeq} \left(\cO(\cE)[-1], Q + \{I,-\} \right) .
\]
\end{dfn}

\begin{dfn}
Let $(E, Q,\omega, I)$ be a classical field theory 
A {\bf strict action} of a super Lie algebra $\fg$ on $(E, Q,\omega, I)$ is a map of super dg Lie algebras
\[
\rho\colon \fg \to \left(\oloc(E)[-1] , \{-,-\}_\omega, Q + \{I,-\}_\omega\right) .
\]
More generally, an $L_\infty$ {\bf action} is an $\infty$-morphism of super dg Lie algebras
\[
\rho\colon \fg \rightsquigarrow \left(\oloc(E)[-1] , \{-,-\}_\omega, Q + \{I,-\}_\omega\right) .
\]
\brian{maybe point to appendix where we can fix conventions for $\infty$-maps}
\end{dfn}

@@

\begin{dfn}
Let $(E, Q, \omega, I)$ be a classical field theory on $M$.
The {\bf classical factorization algebra of observables} $\Obs$ assigns to an open set $U \subset M$ the commutative dg algebra
\[
\Obs(U) = \left(\cO(\cE(U)) , Q + \{I,-\}\right) .
\]
\end{dfn}

@@

\section{Functional analysis}

@@

If $E$ is a vector bundle, let $E^!$ denote the ``Verdier dual" vector bundle defined by $E^* \otimes {\rm Dens}_M$, where $E^*$ is the usual linear dual vector bundle. 
For an open set $U \subset M$ let 
\[
\cE(U)^\vee = \Bar{\cE}^!_c(U)
\]
be the continuous, or distributional dual, to $\sE(U)$.

@@

\begin{dfn}
Let $E$ be a vector bundle on $M$ and $U \subset M$.
The completed algebra of functions on $\cE(U)$ is
\[
\cO(\cE(U)) = \prod_{n = 0}^\infty {\rm Hom}_{\rm CVS} \left(\cE(U)^{\Hat{\otimes}_\beta n}, \CC\right)_{S_n} .
\]
\end{dfn}

@@

@@

\begin{dfn}
A {\bf differentiable pro-cochain complex} is a differentiable cochain complex $V$ with a filtration
\[
\cdots \to F_{n-1} V \to F_{n} V \to F_{n+1}V \to \cdots
\]
where each map is a monomorphism in each cohomological degree and such that the canonical maps $V \to V / F_n V$ induce a quasi-isomorphism $V \to \lim V / F_n V$. 
\end{dfn}

>>>>

A local functional induces an endomorphism $\{I,-\}$ on the space of all local functionals $\oloc(E)$. 
It also induces an endomorphism on the larger space of {\em all} functionals $\cO(\cE)$, see Definition \ref{dfn: fnl} in the appendix. 
The classical master equation implies that the operator $Q + \{I,-\}$ squares to zero on $\cO(\cE)$, and hence every classical field theory defines a cochain complex
\[
\left(\cO(\cE), Q + \{I,-\}\right) .
\]
In fact, this has the structure of a differentiable pro-cochain complex, see Definition \ref{dfn: pro}. 
We will refer to this as the {\bf classical BV complex} of the theory.

@@

Note that a map of classical field theories induces a map of BV complexes, that is, a map of pro-cochain complexes:
\[
F^*\colon \left(\cO (\cE)[-1], Q + \{I,-\} \right) \to \left(\cO (\cE')[-1], Q' + \{I',-\} \right) .
\]
This allows us to make the following definition of an equivalence between classical theories.

\begin{dfn} \label{equivalence_def}
A morphism of classical field theories $F\colon (E, Q, \omega, I) \to (E', Q', \omega', I')$ is an {\bf equivalence} if it induces a quasi-isomorphism of differentiable pro-cochain complexes
\[
F^* \colon  \left(\cO(\cE')[-1], Q' + \{I',-\} \right) \xto{\simeq} \left(\cO(\cE)[-1], Q + \{I,-\} \right) .
\]
\end{dfn}

For a short background on homological algebra with differentiable pro-cochain complexes, including the notion of quasi-isomorphism, we refer to Appendix \ref{appx: top}.
For a more thorough introduction, and for which our conventions are based on, we refer to \cite{CG1}.

\begin{dfn}
Let $(E, Q,\omega, I)$ be a classical field theory 
A {\bf strict action} of a super Lie algebra $\fg$ on $(E, Q,\omega, I)$ is a map of super dg Lie algebras (in differentiable pro-cochain complexes)
\[
\rho\colon \fg \to \left(\oloc(E)[-1] , \{-,-\}_\omega, Q + \{I,-\}_\omega\right) .
\]
More generally, an $L_\infty$ {\bf action} is an $\infty$-morphism of super dg Lie algebras
\[
\rho\colon \fg \rightsquigarrow \left(\oloc(E)[-1] , \{-,-\}_\omega, Q + \{I,-\}_\omega\right) .
\]
\brian{maybe point to appendix where we can fix conventions for $\infty$-maps}
\end{dfn}

@@

\begin{dfn}
Let $(E, Q, \omega, I)$ be a classical field theory on $M$.
The {\bf classical factorization algebra of observables} $\Obs$ assigns to an open set $U \subset M$ the commutative dg algebra (in differentiable pro-cochain complexes)
\[
\Obs(U) = \left(\cO(\cE(U)) , Q + \{I,-\}\right) .
\]
\end{dfn}

Notice that the BV complex we defined in the previous section is simply the global sections of the factorization algebra along $M$.

@@

\section{Functional analysis} \label{appx: top}

@@

If $E$ is a vector bundle, let $E^!$ denote the ``Verdier dual" vector bundle defined by $E^* \otimes {\rm Dens}_M$, where $E^*$ is the usual linear dual vector bundle. 
For an open set $U \subset M$ let 
\[
\cE(U)^\vee = \Bar{\cE}^!_c(U)
\]
be the continuous, or distributional, dual to $\cE(U)$.

\brian{recall definition of CVS. all our familiar spaces above are in $\CVS$. talk about tensor products.}

@@

\begin{dfn}\label{dfn: fnl}
Let $E$ be a vector bundle on $M$ and $U \subset M$.
The {\bf completed algebra of functions} on $\cE(U)$ is
\[
\cO(\cE(U)) = \prod_{n = 0}^\infty {\rm Hom}_{\rm CVS} \left(\cE(U)^{\Hat{\otimes}_\beta n}, \CC\right)_{S_n} .
\]
On global sections, we use the notation $\cO(\cE) = \cO(\cE(M))$. 
\end{dfn}

@@

\brian{can't do cokernels in CVS, blah blah}

@@

\begin{dfn}\label{dfn: pro}
A {\bf differentiable pro-cochain complex} is a differentiable cochain complex $V$ with a filtration
\[
\cdots \to F_{n-1} V \to F_{n} V \to F_{n+1}V \to \cdots
\]
where each map is a monomorphism in each cohomological degree and such that the canonical maps $V \to V / F_n V$ induce a quasi-isomorphism $V \to \lim V / F_n V$. 
\end{dfn}

\begin{lem}
If $(E, \omega, Q, I)$ is the data of a classical theory on $M$, then the BV complex
\[
\left(\cO(\cE) , Q + \{I,-\}\right)
\]
is a differentiable pro-cochain complex.
More generally, the classical factorization algebra of observables $\Obs$ is a factorization algebra in differentiable pro-cochain complexes. 
\end{lem}
